---
title: "rintrinio-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{package_name-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: ../refs.bib
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Introduction to rintrinio

The purpose of rintrinio is to take the data from Intrinio [@intrinio] and make it extraordinarily easy to move to a format for analysis in R [@R].

This document introduces you to the functions included in this package.

## Functions
```{r setup, include=FALSE}
suppressPackageStartupMessages(library(IntrinioSDK))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(devtools))
suppressMessages(load_all())

api_key <- 'OjhlMjhjNTBmY2IyMWJiMWE0MTExYjQwNWZmZTVkZWM1'
```

The four functions in the package are as follows:

- `gather_financial_statement_time_series()` to compare a single company's financial statements over time
- `gather_financial_statement_company_compare()` to compare multiple company's financial statements in a single period
- `gather_stock_time_series()` to gather a time series of stock price information
- `gather_stock_returns()` to gather returns of stocks over time

### Time Series Financial Statement Analysis with `gather_financial_statement_time_series()`

`gather_financial_statement_time_series()` takes in information that would be spread across multiple lines when querying the Intrinio API directly, and puts it into a function that by default returns a dataframe that is ready to be used for analysis. This function should be used for time series analysis of financial statements (income statement, balance sheet, or cash flow statement)

### Cross-Company Financial Statement Analysis with `gather_financial_statement_company_compare()`

### Time Series Stock Analysis with `gather_stock_time_series()`

### Understand Stock Returns with `gather_stock_returns()`

# References